---
title: "Lab 00 - Hello IDS!"
author: "Aimee Tumblety"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Freddie Elson", "Felix Ainsley", "Aimee Tumblety", 
           "Katya Cheltsova", "kayleigh Innes"),
  github_username = c("mcgregors-garden", "freddoderfisch","aimeet05", "fjainsley", 
                      "katya/c", "Kayleighinnes"),
  colour = c("powderblue", "orange", "blue", 
             "purple", "orchid", "green"),
  hobby = c("Hopping", "gym", "guitar", 
            "table tennis", "piano", "Film"),
  favourite_number = c(2, 7, 4, 13, 4, 69)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


 Plot shows a bar chart, each bar labelled with each persons GitHub username, height of bar shows favorite number and color of bar shows favorite color
### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub Username", 
          y = "Favorite Number",
          title = "Team Data")
```

Command Labs() allows to add titles for x-axis, y-axis, main title.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

Graph should be a table instead, shows info clearly.
